\section{Case Studies and Examples}
\subsection{Caryn AI}
CarynAI \cite{lorenz2023influencers}, a chatbot designed to replicate the personality and interactions of its creator, Caryn Marjorie. Caryn Marjorie wanted to talk to as many of her followers as she could — so she made an AI clone of herself. The developers dedicated over 2,000 hours to meticulously design and code Caryn's language and personality into an immersive Al experience. Using her unique voice, captivating persona, and distinctive behavior, Caryn Al brings a dynamic, one-of-a-kind interaction that feels like you're talking directly to Caryn herself. One safeguard is trying to limit the amount of time a user is allowed to chat with CarynAI. To keep users from becoming addicted, CarynAI is programmed to wind down conversations after about an hour, encouraging users to pick back up later. But there is no hard time limit on use, and some users are spending hours speaking to CarynAI per day, according to Marjorie's manager, Ishan Goel. However, access to this version of CarynAI was interrupted when the chief executive of Forever Voices was arrested for attempted arson.
\subsection{LivingAI Emo Pet}
Like a loyal companion, Emo cheers you up with music, dance movements, and online games! Emo is also a great helper that wakes you up, turns on the light, takes pictures and answers to your questions, for a truly life-like pet on your desktop! Built with multiple sensors and cutting-edge techs, Emo is a cool desktop AI robot pet with character that can self-explore the world and react to you with 1000+ faces and movements. Living AI systems can perpetuate gender, racial, or socioeconomic biases, leading to discriminatory outcomes in areas such as hiring, lending, and criminal justice.
